---
title: "Medical Cost Report"
author: "Xiuru Ying"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# Introduction

Medical Cost Personal Dataset is a dataset available at kaggle.com at Miri Choi's profile. The data explains the cost of a small sample of the US population's medical insurance costs based on some attributes, including age, sex, BMI, number of children, region, and smoking habits.

The objectives of the analyses are to explore the roles attributes play in medical insurance costs among the US population.



```{r, load-data}
here::i_am("report.Rmd")
data <- readRDS(
  file = here::here("output/data_clean.rds")
)
```

# Tabular analysis

Characteristics of the `r nrow(data)` samples from the Medical Cost Personal dataset are displayed in the table below.

```{r, table1}
table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one
```

# Graphical analysis

Below we report a scatter plot of individual medical costs billed by health insurance as a function of the number of children covered by health insurance. 

```{r, plot-data}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/scatterplot.png")
)
```












